Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-29 docs/ms.tex
Update ms.tex

The typical procedure of weak lensing analysis usually include ellipticity measurement,shear inference,mass profile reconstruction.
The measurement of galaxy shapes  is  the first step  of weak gravitational lensing analysis,since it's the direct observable
that relates with tangential shear.However in this paper we only concern about how to infere shear from galaxy ellipticity
in a hierachical way.Therefore in our simulation we set up an simple toy model in which we have the observed ellipticity as data,and the only measurement error we consider 
is a Gaussian noise add on the true lensed ellipticity.We suppose there is a uniform shear acting on one all the galaxies in sky patch,

>>>>

The typical procedure of weak lensing analysis usually include ellipticity measurement,shear inference,mass profile reconstruction.
The measurement of galaxy shapes  is  the first step  of weak gravitational lensing analysis,since it's the direct observable
that relates with tangential shear.However in this paper we only concern about how to infere shear from galaxy ellipticity
in a hierachical way.Therefore in our simulation we set up a simple toy model in which we have the observed ellipticity as data,and the only measurement error we consider 
is a Gaussian noise add on the true lensed ellipticity.We suppose there is a uniform shear acting on one all the galaxies in sky patch,
